---
title: "Tracking Reuse Tool"
author: "Filippo Accordino"
date: "2025-03-20"
output:
  html_document: default
  pdf_document: default
editor_options: 
  chunk_output_type: console
  markdown: 
    wrap: 72
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

# Reuse of data of CESSDA Service Providers (archives)

collection in english language only

vers. 1.2 optimized for UK Data Service 19 march 2025

Related publication: Accordino, F., Luzi, D. and Pecoraro, F. (2025),
"Challenges in tracking archive’s data reuse in social sciences",
Digital Library Perspectives, Vol. ahead-of-print No. ahead-of-print.
<https://doi.org/10.1108/DLP-07-2024-0112>

Author of the script: Filippo Accordino Institute for Research on
Population and Social Policies - National Research Council, Rome - Italy
DASSI - Data Archive for Social Sciences in Italy
[f.accordino\@irpps.cnr.it](mailto:f.accordino@irpps.cnr.it){.email}
<https://orcid.org/0000-0002-4245-0654>

Licence: CC BY-NC-SA 4.0

IMPORTANT NOTES

For details on CESSDA metadata, see CMM CESSDA Metadata Model -Version
1.0 (15 November 2019)- <doi:10.5281/zenodo.3543756>

For details on Scopus metadata, see Article Metadata Views,
<https://dev.elsevier.com/sd_article_meta_views.html>

This tool need a Scopus API key, see
<https://dev.elsevier.com/apikey/manage>

```{r}
# insert your Scopus APIkey, see https://dev.elsevier.com/apikey/manage
apiKey <- ""
```

## To start

```{r message=FALSE, warning=FALSE}
rm(list = ls())
library(httr)
library(tibble)
library(dplyr)
library(tidyverse)
library(jsonlite)
library(rscopus)
library(tidyquery)
```

Creating a folder for the output

```{r}
if (!dir.exists("results")) {
  dir.create("results")
}
```

## Output: files with results

| Name | Description |
|------------------------------------|------------------------------------|
| results/Scopus_CDC_sub.csv | Overview of all citations with Scopus and SP metadata |
| results/group_by_cited_DOI_distribution.csv | References frequency for cited studies |
| results/group_by_study_topics.csv | Grouping by data topic. Each cited study can have more than one assigned topic |
| results/group_by_citing_publications.csv | Publications citing SP data |
| results/group_by_citing_publications_number.csv | Frequency of references to datasets in publications |
| results/group_by_citing_publications_byYear.csv | Grouping citing publications by year |
| results/group_by_time_span.csv | Time span study/paper publication |
| results/group_by_citing_publications_subject_groupBy.csv | Citing publications by subject, using ASJC classification |
| results/data_creators_unnest_creators_type.csv | Cited studies by creators' type (university, organization) |

## Extraction of DOIs of the selected Service Provider

```{r}
SP01 <- "Austrian%20Social%20Science%20Data%20Archive%20%28AUSSDA%29"
SP02 <- "Czech%20Social%20Science%20Data%20Archive%20%28%C4%8CSDA%29"
SP03 <- "DASSI%20-%20Data%20Archive%20for%20Social%20Sciences%20in%20Italy"
SP04 <- "Danish%20National%20Archives%20%28DNA%29"
SP05 <- "FORS%20-%20Swiss%20Centre%20of%20Expertise%20in%20the%20Social%20Sciences"
SP06 <- "Finnish%20Social%20Science%20Data%20Archive%20%28FSD%29"
SP07 <- "GESIS%20-%20Leibniz%20Institute%20for%20the%20Social%20Sciences"
SP08 <- "HumMingBird"
SP09 <- "PROGEDO"
SP10 <- "PROGEDO%3A%20Center%20for%20Socio-Political%20Data%20%28CDSP%29"
SP11 <- "Portuguese%20Archive%20of%20Social%20Information%20%28APIS%29"
SP12 <- "Sikt%20-%20Norwegian%20Agency%20for%20Shared%20Services%20in%20Education%20and%20Research"
SP13 <- "Slovak%20Archive%20of%20Social%20Data%20%28SASD%29"
SP14 <- "Slovenian%20Social%20Science%20Data%20Archives%20%28ADP%29"
SP15 <- "SoDaNet%20-%20Greek%20Research%20Infrastructure%20for%20Social%20Science"
SP16 <- "Social%20Sciences%20and%20Digital%20Humanities%20Archive%20%28SODHA%29"
SP17 <- "Swedish%20National%20Data%20Service%20%28SND%29"
SP18 <- "UK%20Data%20Service"

SP <- SP18 # choose your Service Provider from the list below
```

List of Service Providers

-   SP01=AUSSDA

-   SP02=CSDA

-   SP03=DASSI

-   SP04=DNA

-   SP05=FORS

-   SP06=FSD

-   SP07=GESIS

-   SP08=HumMingBird

-   SP09=PROGEDO

-   SP10=PROGEDO CDSP

-   SP11=APIS

-   SP12=Sikt

-   SP13=SASD

-   SP14=ADP

-   SP15=SoDaNet

-   SP16=SODHA

-   SP17=SND

-   SP18=UK Data Service

## Extraction of Studies' DOI

Using: CESSDA data catalogue search API, available at:
<https://api.tech.cessda.eu/>

```{r}
all_variable <- c()

SPdata_en <- data.frame(matrix(nrow = 0, ncol = 0))
"colnames(SPdata_en) = colonne"

start_value <- 0
end_value <- 9400

for (i in 1:10) {
  for (i in seq(start_value, end_value, by = 200)) {
    string <- paste("https://datacatalogue.cessda.eu/api/DataSets/v2/search?publishers=", SP, "&limit=200&offset=", i, "&metadataLanguage=en")
    res1 <- GET(gsub(" ", "", string))
    CDC1 <- fromJSON(rawToChar(res1$content))
    if (as.matrix(CDC1$ResultsCount$retrieved) > 0) {
      CDC1_as_tibble <- as_tibble(CDC1$Results)
      SPdata_en <- bind_rows(SPdata_en, CDC1_as_tibble)
      "SPdata_en[nrow(SPdata_en) + 1,] <- CDC1_as_tibble
      variable <- as.matrix(CDC1$Results$id)
      all_variable <- append(all_variable, variable)"
    }
  }
}

SPdata_en_distinct <-
  distinct(SPdata_en, id, .keep_all = TRUE) # to eliminate duplicates

remove(SPdata_en) # removing of SPdata_en to save space

SPdata_en <- SPdata_en_distinct # renaming
rm(SPdata_en_distinct)
```

Creating a subset of CDC metadata to analyse

```{r}
SPdata_en_sel <-
  SPdata_en[, c(
    "pidStudies",
    "classifications",
    "titleStudy",
    "creators",
    "publicationYear",
    "id"
  )]
```

Retrieving PID/DOI of the studies collected in the SP

-   pidStudies, CMM no. 1.1.10.4

```{r}
SPdata_en_sel_unnest <-
  unnest_wider(SPdata_en_sel,
    col = c("pidStudies"),
    names_repair = "universal"
  )

SPdata_en_sel_unnest$agency <- NULL # eliminating column

SPdata_en_sel_unnest <-
  unnest_wider(SPdata_en_sel_unnest,
    col = c("pid"),
    names_sep = "[_]",
    names_repair = "universal"
  )

SPdata_en_sel_unnest[1] <- NULL # eliminating column
colnames(SPdata_en_sel_unnest)[1] <- "DOI" # renaming

SPdata_DOI_list <-
  as.list(na.omit(SPdata_en_sel_unnest$DOI)) # creating DOIs list (excluding studies without DOI, NA)
  ```

Remove objects to make space

```{r}
rm(
  CDC1,
  CDC1_as_tibble,
  res1
)
```

## Tracking the data reuse on Scopus Indexed Publications

Using:

1.  Muschelli, J. (2019), “Rscopus: Scopus database ‘API’ interface”, R
    package (Version 0.6.6.) [Computer software], available at:
    <https://CRAN.R-project.org/package=rscopus>

2.  Elsevier scopus APIs”, available at:
    <https://dev.elsevier.com/sc_apis.html>

```{r}
Scopus_df <- data.frame()

for (i in SPdata_DOI_list) {
  query <- gsub(" ", "", paste("REF(", i, ")"))

  api_query <-
    scopus_search(
      query = query,
      api_key = apiKey,
      count = 199,
      view = c("STANDARD"),
      start = 0,
      verbose = TRUE,
      max_count = 8000,
      http = "https://api.elsevier.com/content/search/scopus",
      headers = NULL,
      wait_time = 0
    )

  if (api_query$total_results > 0) {
    entries_df <-
      gen_entries_to_df(api_query$entries, scrub = FALSE)

    entries_df <-
      as.data.frame(entries_df$df)

    entries_df$cited_DOI <- i

    Scopus_df <- bind_rows(Scopus_df, entries_df)
  }
}
```

Creating a subset of Scopus metadata

```{r}
data.frame(colnames(Scopus_df))

Scopus_df_sel <-
  Scopus_df[, c(
    "dc:identifier", # DOI
    "dc:title", # Article Title
    "prism:publicationName", # Source title
    "prism:doi", # Document Object Identifier
    "prism:coverDate", # Publication date (YYYY-MM-DD)
    "cited_DOI" # cited study
  )]
```

Convert Publication date (YYYY-MM-DD) in '%Y' format

```{r}
colnames(Scopus_df_sel)[5] <- "year"
Scopus_df_sel$year <-
  as.Date(Scopus_df_sel$year)
Scopus_df_sel$year <-
  as.numeric(format(Scopus_df_sel$year, "%Y"))
```

Merging SP and Scopus metadata

```{r}
Scopus_CDC <-
  left_join(Scopus_df_sel, SPdata_en_sel_unnest,
    by = c(cited_DOI = "DOI"),
    copy = FALSE
  ) # we obtain all citations.
# each publication can cite multiple SP datasets.
# see metadata below
```

| Field | Source | Description |
|------------------------|------------------------|------------------------|
| dc:identifier | Scopus | DOI |
| dc:title | Scopus | Article Title |
| prism:publicationName | Scopus | Source title |
| prism:doi | Scopus | Document Object Identifie |
| year | Scopus | Publication date (YYYY-MM-DD) (retrieved from prism:coverDate) |
| cited_DOI | CESSDA | DOI of cited SP study |
| classifications | CESSDA | Study Topic (controlled), CMM 1.2.2 |
| titleStudy | CESSDA | Study Title, CMM 1.1.3 |
| creators | CESSDA | Principal Investigator Reference, CMM 1.1.7 |
| publicationYear | CESSDA | Publication Year (controlled [YYYY]), CMM no. 1.1.9 |
| id | CESSDA | \>\> id of CESSDA Data Catalogue |

```{r}
Scopus_CDC_sub <-
  Scopus_CDC[, c(1:6, 11, 8, 10)] # overview of all citations with Scopus and SP metadata

write.csv2(Scopus_CDC_sub,
  file = "results/Scopus_CDC_sub.csv"
)
```

## Analysis of data

1)  Grouping by cited studies' DOI Study PID, CMM no. 1.1.10.4

```{r}
group_by_cited_DOI <-
  Scopus_CDC %>%
  group_by(cited_DOI) %>%
  tally(sort = TRUE, name = "Frequency_of_references")

group_by_cited_DOI <-
  group_by_cited_DOI %>%
  left_join(select(SPdata_en_sel_unnest, DOI, titleStudy),
    by = c(cited_DOI = "DOI")
  )
```

```{r}
group_by_cited_DOI_distribution <-
  group_by_cited_DOI %>%
  group_by(Frequency_of_references) %>%
  tally(name = "Cited_datasets_no.") # Study citations distribution

group_by_cited_DOI_distribution <-
  group_by_cited_DOI %>%
  group_by(group_by_cited_DOI$Frequency_of_references) %>%
  tally(name = "Cited_datasets_no.") # Study citations distribution

colnames(group_by_cited_DOI_distribution)[1] <- "Frequency of references"

group_by_cited_DOI_distribution$Cited_datasets_ratio <-
  round(
    group_by_cited_DOI_distribution$Cited_datasets_no. /
      sum(group_by_cited_DOI_distribution$Cited_datasets_no.) * 100,
    digits = 2
  )

write.csv2(group_by_cited_DOI_distribution,
  file = "results/group_by_cited_DOI_distribution.csv"
) # References frequency for cited studies:
```

2)  Grouping by data topics
    -   Study Topic (controlled), CMM 1.2.2

```{r}
group_by_cited_DOI_topic <-
  left_join(group_by_cited_DOI,
    SPdata_en_sel_unnest[, c("DOI", "classifications")],
    by = c(cited_DOI = "DOI"),
    copy = FALSE
  )

group_by_cited_DOI_topic <-
  unnest(group_by_cited_DOI_topic,
    col = c("classifications"),
    names_sep = "[_]",
    names_repair = "universal"
  )

colnames(group_by_cited_DOI_topic)[7] <- "classifications.term"

group_by_cited_DOI_topic_SUM <-
  group_by_cited_DOI_topic %>%
  group_by(classifications.term) %>%
  summarize(sum = sum(Frequency_of_references))

# Grouping by CESSDA Controlled Vocabulary for CESSDA Topic Classification,
# https://vocabularies.cessda.eu/vocabulary/TopicClassification
# Version 4.2.2 - Date of publication  2022-02-02

CESSDA_topic <- read.csv2("CESSDA_topic.csv")

colnames(CESSDA_topic)[1] <- "Topic_1st_level"

group_by_cited_DOI_topic_SUM <-
  left_join(group_by_cited_DOI_topic_SUM, CESSDA_topic,
    by = c(classifications.term = "sub1"),
    copy = FALSE
  )

group_by_cited_DOI_topic_SUM_1st_level <-
  group_by_cited_DOI_topic_SUM %>%
  group_by(Topic_1st_level) %>%
  summarize(sum = sum(sum))

group_by_cited_DOI_topic_SUM_1st_level$ratio <-
  group_by_cited_DOI_topic_SUM_1st_level$sum / sum(group_by_cited_DOI_topic_SUM_1st_level$sum) * 100

group_by_cited_DOI_topic_SUM_1st_level$ratio <-
  round(group_by_cited_DOI_topic_SUM_1st_level$ratio,
    digits = 2
  )

write.csv(group_by_cited_DOI_topic_SUM_1st_level,
  file = "results/group_by_study_topics.csv"
) # grouping by data topic.
# Each cited study can have more than one assigned topic
```

Grouping by CESSDA Controlled Vocabulary for CESSDA Topic Classification

<https://vocabularies.cessda.eu/vocabulary/TopicClassification> Version
4.2.2 - Date of publication 2022-02-02

```{r}
CESSDA_topic <- read.csv2("CESSDA_topic.csv")

colnames(CESSDA_topic)[1] <- "Topic_1st_level"

group_by_cited_DOI_topic_SUM <-
  left_join(group_by_cited_DOI_topic_SUM, CESSDA_topic,
    by = c(classifications.term = "sub1"),
    copy = FALSE
  )

group_by_cited_DOI_topic_SUM_1st_level <-
  group_by_cited_DOI_topic_SUM %>%
  group_by(Topic_1st_level) %>%
  summarize(sum = sum(sum))

group_by_cited_DOI_topic_SUM_1st_level$ratio <-
  group_by_cited_DOI_topic_SUM_1st_level$sum / sum(group_by_cited_DOI_topic_SUM_1st_level$sum) * 100

group_by_cited_DOI_topic_SUM_1st_level$ratio <-
  round(group_by_cited_DOI_topic_SUM_1st_level$ratio,
    digits = 2
  )

write.csv(group_by_cited_DOI_topic_SUM_1st_level,
  file = "results/group_by_study_topics.csv"
) # grouping by data topic.
# Each cited study can have more than one assigned topic
```

5.  Grouping by citing publications' DOI

    Publications citing SP data and frequency of references to datasets

-   Document Object Identifier, Article Metadata Views

```{r}
group_by_citing_publications <-
  Scopus_df_sel %>%
  group_by(`dc:identifier`) %>%
  tally(name = "n of cited dataset") # sum #n of datasets cited for each publication

write.csv2(group_by_citing_publications,
  file = "results/group_by_citing_publications.csv"
)

group_by_citing_publications_number <-
  group_by_citing_publications %>%
  group_by(`n of cited dataset`) %>%
  tally(name = "n of pubb citing") # sum # n of publications citing n. of datasets

group_by_citing_publications_number$CPratio <-
  round(
    (group_by_citing_publications_number$"n of pubb citing" /
      sum(group_by_citing_publications_number$"n of pubb citing") * 100),
    digits = 2
  )

colnames(group_by_citing_publications_number)[1] <- "Frequency of references to data"
colnames(group_by_citing_publications_number)[2] <- "Citing publications no."
colnames(group_by_citing_publications_number)[3] <- "Citing publications %"

write.csv2(group_by_citing_publications_number,
  file = "results/group_by_citing_publications_number.csv"
)
```

6)  Grouping citing publications by year
    -   Publication date (YYYY-MM-DD), Article Metadata Views

```{r}
group_by_citing_publications_byYear <-
  unique(Scopus_df_sel[, c(1, 5)]) %>%
  group_by(`year`) %>%
  tally(name = "n of publications by year") # sum #n of publications citing SP data for each year

write.csv2(group_by_citing_publications_byYear,
  file = "results/group_by_citing_publications_byYear.csv"
)
```

5)  Calculating time span study/paper publication

-   Publication Year (controlled [YYYY]), CMM no. 1.1.9
-   Publication date (YYYY-MM-DD), Publication date (YYYY-MM-DD),
    Article Metadata Views

```{r}
time_span <-
  left_join(Scopus_df_sel[, c("dc:title", "prism:doi", "year", "cited_DOI")],
    SPdata_en_sel_unnest[, c("DOI", "titleStudy", "publicationYear")],
    by = c("cited_DOI" = "DOI"),
    copy = FALSE
  )

time_span$publicationYear <-
  as.Date(time_span$publicationYear, "%Y")
time_span$publicationYear <-
  as.numeric(format(time_span$publicationYear, "%Y"))

time_span$time_span <-
  time_span$year - time_span$publicationYear

group_by_time_span <-
  time_span %>%
  group_by(`time_span`) %>%
  tally(name = "n of publications") # n of publications for each time span (year)

write.csv(group_by_time_span,
  file = "results/group_by_time_span.csv"
)
```

6)  Grouping citing publications by subject

    Using ASJC classification. Each journal can refer to more than one
    ASJC category. Version may 2023 see
    <https://service.elsevier.com/app/answers/detail/a_id/15181/supporthub/scopus/>

```{r}
ASJC_code <- read.csv2(
  file = "scopus_journal_may_2023/ASJC_code.csv"
)
colnames(ASJC_code)[1] <- "ASJC_code"
colnames(ASJC_code)[2] <- "ASJC_category"
colnames(ASJC_code)[3] <- "ASJC_subject_area"

ASJC_Scopus <- read.csv2(
  file = "scopus_journal_may_2023/ASJC_journals_scopus_listMay2023.csv"
)
colnames(ASJC_Scopus)[1] <- "Source_title"

colnames(ASJC_Scopus)[2] <- "ASJC_1"
colnames(ASJC_Scopus)[3] <- "ASJC_2"
colnames(ASJC_Scopus)[4] <- "ASJC_3"
colnames(ASJC_Scopus)[5] <- "ASJC_4"
colnames(ASJC_Scopus)[6] <- "ASJC_5"
colnames(ASJC_Scopus)[7] <- "ASJC_6"
colnames(ASJC_Scopus)[8] <- "ASJC_7"
colnames(ASJC_Scopus)[9] <- "ASJC_8"
colnames(ASJC_Scopus)[10] <- "ASJC_9"
colnames(ASJC_Scopus)[11] <- "ASJC_10"
colnames(ASJC_Scopus)[12] <- "ASJC_11"
colnames(ASJC_Scopus)[13] <- "ASJC_12"
colnames(ASJC_Scopus)[14] <- "ASJC_13"

data.frame(colnames(ASJC_Scopus))
ASJC_Scopus_1_2 <- ASJC_Scopus[, c(1, 2)]
ASJC_Scopus_1_3 <- ASJC_Scopus[, c(1, 3)]
ASJC_Scopus_1_4 <- ASJC_Scopus[, c(1, 4)]
ASJC_Scopus_1_5 <- ASJC_Scopus[, c(1, 5)]
ASJC_Scopus_1_6 <- ASJC_Scopus[, c(1, 6)]
ASJC_Scopus_1_7 <- ASJC_Scopus[, c(1, 7)]
ASJC_Scopus_1_8 <- ASJC_Scopus[, c(1, 8)]
ASJC_Scopus_1_9 <- ASJC_Scopus[, c(1, 9)]
ASJC_Scopus_1_10 <- ASJC_Scopus[, c(1, 10)]
ASJC_Scopus_1_11 <- ASJC_Scopus[, c(1, 11)]
ASJC_Scopus_1_12 <- ASJC_Scopus[, c(1, 12)]
ASJC_Scopus_1_13 <- ASJC_Scopus[, c(1, 13)]

colnames(ASJC_Scopus_1_2)[2] <- "ASJC"
colnames(ASJC_Scopus_1_3)[2] <- "ASJC"
colnames(ASJC_Scopus_1_4)[2] <- "ASJC"
colnames(ASJC_Scopus_1_5)[2] <- "ASJC"
colnames(ASJC_Scopus_1_6)[2] <- "ASJC"
colnames(ASJC_Scopus_1_7)[2] <- "ASJC"
colnames(ASJC_Scopus_1_8)[2] <- "ASJC"
colnames(ASJC_Scopus_1_9)[2] <- "ASJC"
colnames(ASJC_Scopus_1_10)[2] <- "ASJC"
colnames(ASJC_Scopus_1_11)[2] <- "ASJC"
colnames(ASJC_Scopus_1_12)[2] <- "ASJC"
colnames(ASJC_Scopus_1_13)[2] <- "ASJC"

ASJC_Scopus_rbind <- rbind(
  ASJC_Scopus_1_2,
  ASJC_Scopus_1_3,
  ASJC_Scopus_1_4,
  ASJC_Scopus_1_5,
  ASJC_Scopus_1_6,
  ASJC_Scopus_1_7,
  ASJC_Scopus_1_8,
  ASJC_Scopus_1_9,
  ASJC_Scopus_1_10,
  ASJC_Scopus_1_11,
  ASJC_Scopus_1_12,
  ASJC_Scopus_1_13
)

colnames(ASJC_Scopus_rbind)[2] <- "ASJC_code"

rm(
  ASJC_Scopus_1_2,
  ASJC_Scopus_1_3,
  ASJC_Scopus_1_4,
  ASJC_Scopus_1_5,
  ASJC_Scopus_1_6,
  ASJC_Scopus_1_7,
  ASJC_Scopus_1_8,
  ASJC_Scopus_1_9,
  ASJC_Scopus_1_10,
  ASJC_Scopus_1_11,
  ASJC_Scopus_1_12,
  ASJC_Scopus_1_13
)

ASJC_Scopus_rbind <-
  merge(
    x = ASJC_Scopus_rbind,
    y = ASJC_code,
    by = "ASJC_code"
  )

Scopus_df_sel_publication <-
  as.data.frame(unique(Scopus_df_sel[, c(1, 3)]))

colnames(Scopus_df_sel_publication)[2] <- "publicationName"

citing_publications_subject <-
  left_join(Scopus_df_sel_publication,
    ASJC_Scopus_rbind,
    by = c("publicationName" = "Source_title")
  )

group_by_citing_publications_subject_groupBy <-
  citing_publications_subject %>%
  group_by(ASJC_subject_area) %>%
  tally(name = "n") # sum

write.csv(group_by_citing_publications_subject_groupBy,
  file = "results/group_by_citing_publications_subject_groupBy.csv"
)
```

7)  Grouping cited studies by creators' type (university, organization)

-   Principal Investigator Reference, CMM 1.1.7

```{r}
data.frame(colnames(group_by_cited_DOI))

data_creators <-
  group_by_cited_DOI %>%
  left_join(select(SPdata_en_sel_unnest, DOI, creators),
    by = c(cited_DOI = "DOI")
  )

data_creators_unnest <-
  unnest(data_creators,
    col = c("creators"),
    names_sep = "[_]",
    names_repair = "universal"
  )

colnames(data_creators_unnest)[4] <- "creators"

# university#############
data_creators_unnest_university <-
  query("SELECT * FROM data_creators_unnest
        WHERE LOWER(creators) LIKE '%univer%'
        OR LOWER(creators) LIKE '%fakulteta%'
        OR LOWER(creators) LIKE '%college%'
        OR LOWER(creators) LIKE '%school%'
        OR LOWER(creators) LIKE '%hochschule%'")

# organization####
data_creators_unnest_organization <-
  query("SELECT * FROM data_creators_unnest
                    WHERE LOWER(creators) NOT LIKE '%univer%'
                    AND LOWER(creators) NOT LIKE '%fakulteta%'
                    AND LOWER(creators) NOT LIKE '%college%'
                    AND LOWER(creators) NOT LIKE '%school%'
                    AND LOWER(creators) NOT LIKE '%hochschule%'

                    AND (
                    LOWER(creators) LIKE '%institu%'
                    OR LOWER(creators) LIKE '%research%'
                    OR LOWER(creators) LIKE '%forschun%'
                    OR LOWER(creators) LIKE '%agency%'
                    OR LOWER(creators) LIKE '%analys%'
                    OR LOWER(creators) LIKE '%europe%'
                    OR LOWER(creators) LIKE '%statisti%'
                    OR LOWER(creators) LIKE '%commission%'
                    OR LOWER(creators) LIKE '%education%'
                    OR LOWER(creators) LIKE '%ation%'
                    OR LOWER(creators) LIKE '%service%'
                    OR LOWER(creators) LIKE '%department%'
                    OR LOWER(creators) LIKE '%board%'
                    OR LOWER(creators) LIKE '%association%'
                    OR LOWER(creators) LIKE '%office%'
                    OR LOWER(creators) LIKE '%network%'
                    OR LOWER(creators) LIKE '%centr%'
                    OR LOWER(creators) LIKE '%center%'
                    OR LOWER(creators) LIKE '%bureau%'
                    OR LOWER(creators) LIKE '%archiv%'
                    OR LOWER(creators) LIKE '%istat%'
                    OR LOWER(creators) LIKE '%building%'
                    OR LOWER(creators) LIKE '%economic%'
                    OR LOWER(creators) LIKE '%histor%'
                    OR LOWER(creators) LIKE '%council%'

                    OR LOWER(creators) LIKE '%trust%'
                    OR LOWER(creators) LIKE '%ipsos%'
                    OR LOWER(creators) LIKE '%gfk%'
                    OR LOWER(creators) LIKE '%garr%'
                    OR LOWER(creators) LIKE '%cern%'
                    OR LOWER(creators) LIKE '%luiss%'
                    OR LOWER(creators) LIKE '%eurostat%'
                    OR LOWER(creators) LIKE '%oxfam%'
                    OR LOWER(creators) LIKE '%tns gallup%'
                    OR LOWER(creators) LIKE '%ministry%'
                    OR LOWER(creators) LIKE '%library%'
                    OR LOWER(creators) LIKE '%plattform%'
                    OR LOWER(creators) LIKE '%laboratorio%'
                    OR LOWER(creators) LIKE '%census%'
                    OR LOWER(creators) LIKE '%kommission%'
                    OR LOWER(creators) LIKE '%europ%'
                    OR LOWER(creators) LIKE '%eurisko%'
                    OR LOWER(creators) LIKE '%UKDS%'
                    OR LOWER(creators) LIKE '%wissen%'
                    OR LOWER(creators) LIKE '%govern%'
                    OR LOWER(creators) LIKE '%hospital%'
                    OR LOWER(creators) LIKE '%social%'
                    OR LOWER(creators) LIKE '%observa%'
                    OR LOWER(creators) LIKE '%election%'
                    OR LOWER(creators) LIKE '%politi%'

                    OR creators LIKE '%MORI%'
                    OR LOWER(creators) LIKE '%sozialwissenschaftliche studiengesellschaft%'
                    OR LOWER(creators) LIKE '%sonar%'
                    OR LOWER(creators) LIKE '%union%'
                    OR LOWER(creators) LIKE '%Konrad-Adenauer-Stiftung%'
                    OR LOWER(creators) LIKE '%klinik%'
                    OR LOWER(creators) LIKE '%usia%'
                    OR LOWER(creators) LIKE '%divo%'
                    OR LOWER(creators) LIKE '%marplan%'
                    OR LOWER(creators) LIKE '%emnid%'
                    OR LOWER(creators) LIKE '%forsa%'
                    OR LOWER(creators) LIKE '%zuma%'
                    OR LOWER(creators) LIKE '%tarki%'
                    OR LOWER(creators) LIKE '%romanian academy%'
                    )
                    ")

# NOTorgNOTuni####
data_creators_unnest_NOTorgNOTuni <-
  query("SELECT * FROM data_creators_unnest
                    WHERE LOWER(creators) NOT LIKE '%univer%'
                    AND LOWER(creators) NOT LIKE '%fakulteta%'
                    AND LOWER(creators) NOT LIKE '%college%'
                    AND LOWER(creators) NOT LIKE '%school%'
                    AND LOWER(creators) NOT LIKE '%hochschule%'
                    AND LOWER(creators) NOT LIKE '%institu%'
                    AND LOWER(creators) NOT LIKE '%research%'
                    AND LOWER(creators) NOT LIKE '%forschun%'
                    AND LOWER(creators) NOT LIKE '%agency%'
                    AND LOWER(creators) NOT LIKE '%analys%'
                    AND LOWER(creators) NOT LIKE '%europe%'
                    AND LOWER(creators) NOT LIKE '%statisti%'
                    AND LOWER(creators) NOT LIKE '%commission%'
                    AND LOWER(creators) NOT LIKE '%education%'
                    AND LOWER(creators) NOT LIKE '%ation%'
                    AND LOWER(creators) NOT LIKE '%service%'
                    AND LOWER(creators) NOT LIKE '%department%'
                    AND LOWER(creators) NOT LIKE '%board%'
                    AND LOWER(creators) NOT LIKE '%association%'
                    AND LOWER(creators) NOT LIKE '%office%'
                    AND LOWER(creators) NOT LIKE '%network%'
                    AND LOWER(creators) NOT LIKE '%centr%'
                    AND LOWER(creators) NOT LIKE '%center%'
                    AND LOWER(creators) NOT LIKE '%bureau%'
                    AND LOWER(creators) NOT LIKE '%archiv%'
                    AND LOWER(creators) NOT LIKE '%istat%'
                    AND LOWER(creators) NOT LIKE '%building%'
                    AND LOWER(creators) NOT LIKE '%economic%'
                    AND LOWER(creators) NOT LIKE '%histor%'
                    AND LOWER(creators) NOT LIKE '%council%'


                    AND LOWER(creators) NOT LIKE '%trust%'
                    AND LOWER(creators) NOT LIKE '%ipsos%'
                    AND LOWER(creators) NOT LIKE '%gfk%'
                    AND LOWER(creators) NOT LIKE '%garr%'
                    AND LOWER(creators) NOT LIKE '%cern%'
                    AND LOWER(creators) NOT LIKE '%luiss%'
                    AND LOWER(creators) NOT LIKE '%eurostat%'
                    AND LOWER(creators) NOT LIKE '%oxfam%'
                    AND LOWER(creators) NOT LIKE '%tns gallup%'
                    AND LOWER(creators) NOT LIKE '%ministry%'
                    AND LOWER(creators) NOT LIKE '%library%'
                    AND LOWER(creators) NOT LIKE '%plattform%'
                    AND LOWER(creators) NOT LIKE '%laboratorio%'
                    AND LOWER(creators) NOT LIKE '%census%'
                    AND LOWER(creators) NOT LIKE '%kommission%'
                    AND LOWER(creators) NOT LIKE '%europ%'
                    AND LOWER(creators) NOT LIKE '%eurisko%'
                    AND LOWER(creators) NOT LIKE '%UKDS%'
                    AND LOWER(creators) NOT LIKE '%wissen%'
                    AND LOWER(creators) NOT LIKE '%govern%'
                    AND LOWER(creators) NOT LIKE '%hospital%'
                    AND LOWER(creators) NOT LIKE '%social%'
                    AND LOWER(creators) NOT LIKE '%observa%'
                    AND LOWER(creators) NOT LIKE '%election%'
                    AND LOWER(creators) NOT LIKE '%politi%'

                    AND creators NOT LIKE '%MORI%'
                    AND LOWER(creators) NOT LIKE '%sozialwissenschaftliche studiengesellschaft%'
                    AND LOWER(creators) NOT LIKE '%sonar%'
                    AND LOWER(creators) NOT LIKE '%union%'
                    AND LOWER(creators) NOT LIKE '%Konrad-Adenauer-Stiftung%'
                    AND LOWER(creators) NOT LIKE '%klinik%'
                    AND LOWER(creators) NOT LIKE '%usia%'
                    AND LOWER(creators) NOT LIKE '%divo%'
                    AND LOWER(creators) NOT LIKE '%marplan%'
                    AND LOWER(creators) NOT LIKE '%emnid%'
                    AND LOWER(creators) NOT LIKE '%forsa%'
                    AND LOWER(creators) NOT LIKE '%zuma%'
                    AND LOWER(creators) NOT LIKE '%tarki%'
                    AND LOWER(creators) NOT LIKE '%romanian academy%'
                    ")

data_creators_unnest_creators_type <-
  data.frame(rbind
  (data.frame
    (
      query("SELECT sum(n_of_citation) AS 'University' FROM data_creators_unnest_university"),
      query("SELECT sum(n_of_citation) AS 'Organization' FROM data_creators_unnest_organization"),
      query("SELECT sum(n_of_citation) AS 'NOT University NOT Organization' FROM data_creators_unnest_NOTorgNOTuni")
  )))

write.csv(data_creators_unnest_creators_type,
  file = "results/data_creators_unnest_creators_type.csv"
)
```
